Modeling potential JCPOA diversion scenarios with Cyclus

### 2018-05-04 paper.tex
add bibliography

% I don't think Total Monte Carlo should be in quotes

\section{Method}

@@

To pursuit this work, both the Cycamore\cite{cycamore} package and the
CyCLASS\cite{cyclass} have been updated to deal with uncertainty in several
operational parameters of their associated facilities.  Table
\ref{tab:package_uncertainty} summarizes all modificatiosn implemented in the
range of facilities present in Cycamore and CyCLASS.

@@

Package   & Facility   & Parameters                \\
\midrule
Cycamore & Enrichment & Tail Assay                \\
         & Separation & Separation efficiency     \\
         & Storage    & Residence Time            \\
\midrule
CyCLASS  & Reactor    & Cycle Length              \\
         &            & Power                     \\
         &            & Fuel Enrichment (PWR-UOX) \\

@@

It must be noted that for this work, the fuel enrichment was determined by a
fuel fabrication model\cite{leniau} which
calculates the fissile fraction required in the fuel to reach a target
burnup at the end of irradiation. In this study, the uncertainty on the fuel
enrichment is not applied directly on the effective enrichment but on the target
parameter (the burnup), which leads to to a fuel enrichment uncertainty close to
$10\%$.

\section{The Experiment}
\subsection{The Fuel Cycle}
This work aims to assess the impact of the functional uncertainties of a
simple transition as shown in Figure \ref{fig:cycle}, inspired from the EG23 fuel cycle of the Nuclear Fuel Cycle Evaluation and Screening Report\cite{FCO}: a transition from light water reactors fleet loaded
with \glspl{UOX} fuel to a sodium fast reactor fleet loaded \glspl{MOX} fuel, considering an
$1\%/$y growth of the generated power (Figure \ref{fig:power}).
\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[scale=0.31]{cycle.png}
  \caption{Illustration of the material flow between the different facilities,
  with in green each operational parameters associated with an
  uncertainty.}\label{fig:cycle}
\end{figure}

As illustrated in Figure \ref{fig:power}, the transition starts with a fleet
fully composed of \glspl{LWR} loaded with enriched \glspl{UOX} fuel. The actual
transition starts around year 35, with the deployment of \glspl{FBR}, loaded
with \glspl{MOX}, consisting of plutonium blended with natural
uranium. Once the transition to a full \glspl{FBR} fleet is completed, the
\glspl{FBR} fleet is slowly replaced with \glspl{FBR} with a lower breeding
ratio.

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
    \centering
    \includegraphics[scale=0.18]{power.png}
    \caption{Electric power generated over time, with in blue the full production,
        in orange the \glspl{LWR} contribution, in green the hight breeding ratio
        \glspl{FBR} and in red the low breeding ratio \glspl{FBR}.}\label{fig:power}
\end{figure}

The plutonium, required for \glspl{MOX} fabrication, is reprocessed from all
used fuel. At first , it is sourced only from UOX, then used MOX fuel as it becomes
available for reprocessing.

@@

As the number of deployed \glspl{LWR} reactors increases, as each parameters is
sampled once for each facilities, the average length of the cycle (as well as
the number of loaded batches) converges to the reference value.
The fuel enrichment and the tail assay contribution follow a smoother behavior,
so as the total relative uncertainty decrease, their contribution increases over
time.

@@

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
    \centering
    \includegraphics[scale=0.17]{used_fuel}
    \caption{Used fuel inventory.}\label{fig:used_fuel}
\end{figure}
Between year 90 and 120, the \glspl{FBR} deployment speed increases, it has to
compensate the non replacement of the decommissioned \glspl{LWR} as well as
follow the power demand. During this period the needs in plutonium are higher
than its productions, explaining the observed decrease of the total amount, and
the increase associated relative uncertainty.

>>>>

% I don't think Total Monte Carlo should be in quotes
\section{The Experiment}

\subsection{Method}

@@

To pursuit this work, both the Cycamore\cite{cycamore} package\footnote{Low
fidelity facilities package for Cyclus} and the
CyCLASS\footnote{Reactor and Fuel fabrication facility based on
    CLASS\cite{CLASS}  models} have been
updated\cite{mouginot_2018, cyclass} to deal with uncertainty in several
operational parameters of their associated facilities.  Table
\ref{tab:package_uncertainty} summarizes all modification implemented in the
range of facilities present in Cycamore and CyCLASS.

@@

Package   & Facility   & Parameters                \\
\midrule
Cycamore & Separation & Separation efficiency     \\
         & Storage    & Residence Time            \\
\midrule
CyCLASS  & Reactor    & Cycle Length              \\
         &            & Power                     \\
         &            & Fuel Enrichment (PWR-UOX) \\

@@

It must be noted that for this work, the fuel enrichment was determined by a
fuel fabrication model\cite{Leniau2015125} which
calculates the fissile fraction required in the fuel to reach a target
burnup at the end of irradiation. In this study, the uncertainty on the fuel
enrichment is not applied directly on the effective enrichment but on the target
parameter (the burnup), which leads to to a fuel enrichment uncertainty close to
$10\%$.

\subsection{The Fuel Cycle}
This work estimates the impact of the operational parameters uncertainty on a simple
transition (see Figure \ref{fig:cycle}) inspired from the EG23 of the Screening
And Evaluation Group\cite{ES}: a transition from light water reactors fleet
loaded with \glspl{UOX} fuel to a sodium fast reactors fleet loaded \glspl{MOX}
fuel, considering an $1\%/$y grows of the generated power (Figure
\ref{fig:power}).

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[scale=0.31]{cycle.png}
  \caption{Illustration of the material flow between the different facilities,
  with in green each operational parameters associated with an
  uncertainty.}\label{fig:cycle}
\end{figure}

As illustrated on Figure \ref{fig:power}, the transition starts with a fleet
fully composed by \glspl{LWR} loaded with enriched \glspl{UOX} fuel. The actual
transition starts around year 35, with the deployment of \glspl{FBR}, loaded
with Mixed oxide fuel (MOX), consisting of plutonium blended with natural
uranium.

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
    \centering
    \includegraphics[scale=0.18]{power.png}
    \caption{Electric power generated over time, with in blue the full production,
        in orange the \glspl{LWR} contribution, in green the \glspl{FBR}.}\label{fig:power}
\end{figure}

The plutonium, required for the \glspl{MOX} fabrication, is reprocessed from all
used fuel, at first only used UOX, then used MOX fuel as they start to be
available for reprocessing.

@@

As the number of deployed \glspl{LWR} reactors increases, as each parameters is
sampled once for each facilities, the average length of the cycle (as well as
the number of loaded batches) converges to the reference value.
The fuel enrichment contribution follow a smoother behavior, so as the total
relative uncertainty decrease, their contribution increases over time.

@@

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
    \centering
    \includegraphics[scale=0.18]{used_fuel}
    \caption{Used fuel inventory.}\label{fig:used_fuel}
\end{figure}
Between year 90 and 120, the \glspl{FBR} deployment speed increases, it has to
compensate the non replacement of the decommissioned \glspl{LWR} as well as
follow the power demand. During this period the needs in plutonium are higher
than its productions, explaining the observed decrease of the total amount, and
the increase associated relative uncertainty.
